Resolvable Ambiguity

### 2019-07-11 paper/paper.tex
Speling

\section{Conclusion}
In this paper, we introduce the concept of \emph{resolvable
  ambiguity}. A language grammar is resolvably ambiguous if all
ambiguities can be resolved by the end-user at parse time. This
approach departs from the common standpoint that grammars and
syntax definitions of languages must be unambiguous.
%
As part of the new concept, we formalize the fundamental
\emph{resolvable ambiguity problem}, divide it into static and
dynamic parts, and provide solutions for both variants for a
restricted class of languages. Through case studies, we
showe practical applicability of the approach, both for building
new domain-specific languages and for reasoning about existing
general-purpose languages.

>>>>

\section{Conclusion}
In this paper, we introduce the concept of \emph{resolvable
  ambiguity}. A language grammar is resolvably ambiguous if all
ambiguities can be resolved by the end-user at parse time. This
approach departs from the common standpoint that grammars and
syntax definitions of languages must be unambiguous.
%
As part of the new concept, we formalize the fundamental
\emph{resolvable ambiguity problem}, divide it into static and
dynamic parts, and provide solutions for both variants for a
restricted class of languages. Through case studies, we show
practical applicability of the approach, both for building new
domain-specific languages and for reasoning about existing
general-purpose languages.
